%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{bibentry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lipsum}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage[
    hidelinks
]{hyperref}
\usepackage[normalem]{ulem}
\usepackage{xcolor}


\makeatletter
\begingroup
  \catcode`\$=6 %
  \catcode`\#=12 %
  \gdef\href@split$1#$2#$3\\$4{%
    \hyper@@link{$1}{$2}{\uline{$4}}% or \underline
    \endgroup}%
\endgroup
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\usepackage{lastpage}
\rfoot{\thepage/\pageref{LastPage}}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-5pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \vspace{-1pt}
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\projectHeading}[2]{
\vspace{-1pt}
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}





}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{1pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \multirow{2}{*}{\textbf{\LARGE Varad Vaidya}} &  \href{mailto:vaidyavarad2001@gmail.com}{vaidyavarad2001@gmail.com}\\
                               & \href{https://github.com/varadVaidya}{GitHub: varadVaidya} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeHeading
      {Visvesvaraya National Institute of Technology}{Nagpur, India}
      {B.Tech in Mechanical Engineering; CGPA: 8.66}{July 2018 -- May 2022}


%-----------EXPERIENCE-----------------
\section{Research Experience}
 
%------------------ IITD Internship -------------------
    \resumeHeading
      {Obstacle Avoidance using Dynamic Motion Primitives}{Indian Institute of Technology, Delhi}
      {Research Intern}{Apr. 2021 --- Oct. 2021}
      \resumeItemListStart
        \resumeItem{}
          {Implemented Cartesian and joint space dynamic motion primitives on Kuka LBR iiwa in PyBullet for movement reproduction of complex trajectories}
        \resumeItem{}
          {Extended the formulation to include orientation based motion primitives using quaternions for singularity free representation, and demonstrated the spatial and temporal scalability of the system}
        \resumeItem{}
          {Implemented Static and Dynamic Potential Fields to avoid multiple stationery and moving obstacles}
        \resumeItem{}{Reduced the error in the motion primitive's trajectory by extrapolating the obstacle's position and checking its collision with the robot's motion}
      \resumeItemListEnd

%-------------- IISc Internship -----------------------

    \resumeHeading
        {Control of Flexible Manipulator using Deep Reinforcement Learning}{IISc, Bengaluru}
        {Research Intern}{Dec. 2021 --- Present}
        
        \resumeItemListStart
            \resumeItem{}{Studied Reinforcement and Deep Learning to implement Deep Reinforcement Algorithms such as DQN and DDPG on OpenAI and PyBullet environments using pytorch}
            \resumeItem{}{Creating a custom environment to handle dynamics of flexible manipulators }
        \resumeItemListEnd
\vspace{-3mm} % remove some vertical space
%----------- PUBLICATIONS--------------------------
\nobibliography{ref}
 \bibliographystyle{ieeetr}
\section{Publications}

    \resumeItemListStart
        \resumeItem{}{\bibentry{sahayak}}
    \resumeItemListEnd



%-----------PROJECTS-------------------------------
\section{Projects}
%%%%%%%%%%__________VIiLocNAV________%%%%%%%%%%%%%%%%%%%%%%

    \projectHeading
        {Visual Learning-based Optimal Control and Navigation}{Jan. 2022 --- Present}
        \resumeItemListStart
            \resumeItem{}{Created a custom PyBullet environment with Turtlebot2 in PyBullet and implemented PID and iLQR control to reach a provided waypoint}
            \resumeItem{}{Integrating iGibson dataset with our control architecture to enable realistic rendering and interaction with environments}
        \resumeItemListEnd
        
%%%%%%%________SAHAYAK___________%%%%%%%%%%%%%%%%%%
    \projectHeading
        {Sahayak-v3: Product Design}{Dec. 2020 --- Mar. 2021}
        \resumeItemListStart
            \resumeItem{}{Designed the cyber-physical architecture of Sahayak COVID aid bot for autonomous capabilities}
            \resumeItem{}{Modified the CAD model of Sahayak-v2 for robust locomotion in SolidWorks and selected the components mathcing the requirements}
            \resumeItem{}{Added senor models to CAD model and converted entire robot stack to URDF for simulation in Gazebo}
        \resumeItemListEnd        
%%%%%%%%%%--------- FORCE CONTROL----------%%%%%%%%%%%

    \projectHeading
        {Force Control of Manipulators}{Jan. 2021 --- Apr. 2021}
        \resumeItemListStart
            \resumeItem{}{Applied stiffness and kinematic control of planar 2DOF manipulator in Python from scratch}
            \resumeItem{}{Wrote a custom wrapper over PyBullet for robotic manipulators for ease of control, trajectory generation and planning, using SLERP for quaternion interpolation}
            \resumeItem{}{Implemented force control methods like computed torque control and impedance control on UR5 in PyBullet}
        \resumeItemListEnd

%%%%%%%%%%%%_____________ youBot_____________%%%%%%%%%%%  
    \projectHeading
        {Mobile Manipulation using Kuka youBot}{Oct. 2020 --- Nov. 2020}
        \resumeItemListStart
            \resumeItem{}{Designed end-effector trajectory using cubic splines and rotation matrix interpolation for a cube to be picked and placed between two locations}
            \resumeItem{}{Simulated the kinematics of youBot wheeled manipulator, controlled using PI controller, in Python and visualised in CoppeliaSim}
        \resumeItemListEnd
\newpage
%%%%%%%%%___________ 2ARM QUADROTOR________________%%%%%%%
    \projectHeading
        {2 Arm Quadcopter Balance}{Feb. 2020 --- Mar. 2020}
        \resumeItemListStart
            \resumeItem{}{Designed and manufactured a two arm balance for quadcopter balancing using PID control}
            \resumeItem{}{Used MPU 9250 IMU with Arduino Uno to provide PWM signals to BLDC motors}
            \resumeItem{}{Implemented complementary filter to provide accurate estimate of the pitch of the system}
        \resumeItemListEnd

%%%%___________Trajectory generation of planr quadrotor_______________%%%%%%%%%%

    \projectHeading
        {Dynamic Modelling of Quadcopter}{Mar. 2020 --- July. 2020}
        \resumeItemListStart
            \resumeItem{}{Developed a dynamic model of quadcopter in MATLAB controlled using PID controller}
            \resumeItem{}{Implemented a planar quadrotor model in Python from scratch to follow minimum velocity, acceleration and jerk trajectories for point to point navigation}
        \resumeSubHeadingListEnd
\vspace{-3mm}
% --------SKILLS------------
\section{Skills}
    \resumeSubHeadingListStart
        \resumeItem{Programming: }{Python, C, MATLAB, Simulink, \LaTeX}
        \resumeItem{Tools and Software: }{Linux, PyBullet, SolidWorks, OnShape, PyTorch, ANSYS, ROS, Arduino}
        \resumeItem{Misc: }{Git/GitHub, Adobe LightRoom}
    \resumeSubHeadingListEnd
%%%%_____ RELEVENT COURSEWORK_________%%%%%%%%%%%
\section{Relevant Coursework}
    \resumeSubHeadingListStart
        \resumeItem{MOOC: }{\href{https://coursera.org/share/ea3f882b4fcd497819e00607c1e7be82}{Aerial Robotics}, \href{https://coursera.org/share/5d302e73bc18fe9fe2ff152a5bac61ff}{Modern Robotics: Mechanics, Planning, and Control}}
        \resumeItem{Mechanical: }{Industrial Robotics, Control Systems, Finite Element Method, Theorey of Machines I and II}
        \resumeItem{Mathematics: }{Statistical Analysis and Queuing Theory, Integral Transforms and Partial Differential Equations}
    \resumeSubHeadingListEnd

\section{ExtraCurricular}
    \projectHeading{Project Head, IvLabs, VNIT Nagpur}{May. 2020 --- Jul. 2021}
    \resumeSubHeadingListStart
        \resumeItem{}{Led the student body responsible for deciding summer projects for sophomore students}
        \resumeItem{}{Conducted IEEE workshops on SolidWorks and Basic Electronics}
        \resumeItem{}{Guided summer projects related to Control and Dynamics at IvLabs}
    \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}